Cosmic web alignments with the shape, angular momentum and peculiar velocities of dark matter halos

### 2014-02-06 paper/main.tex
interweb alignment at the end
writing on preferential alignment

\title[Vweb \& Tweb]{Cosmic web correlations with the shape, spin and
  peculiar velocties of dark matter halos}  
\author[S. Contreras et al.]{
\parbox[t]{\textwidth}{\raggedright 
  Jaime E. Forero-Romero$^{1}$,
  Sergio Contreras$^{2}$,
  Nelson Padilla$^{2}$ 
}
\vspace*{6pt}\\
$^{1}$Uni A
$^{2}$Uni B
}
\maketitle

@@

{\bf Forero-Romero et al. (2014)} & T-Web & $0.5-1 \hMpc$ & 
filament &$++$ & all masses\hMsun\\
&   & & 
wall & $--$ & all masses\\\hline

{\bf Forero-Romero et al. (2014)} & Vp-Web & $0.5-1 \hMpc$ & 
filament &$?$ & $>10^{12}$\hMsun\\
&   & & 
filament &$?$ & $<10^{12}$\hMsun\\
&   & & 
wall & $?$ & all masses\\\hline

@@

\end{tabular}\\
\caption{Shape alignment with the cosmic web. Summary of theoretical
  results provided by methods comparable to ours.}
\end{table*}

@@

\cite{Codis2012} & Morse Theory \& T-Web & $1-5$ & 
filament & $--$ & $>10^{12}$\hMsun \\

&   & & 
filament & $++$ & $<10^{12}$\hMsun \\

@@

\end{tabular}
\caption{Spin alignment with the cosmic web. Summary of theoretical
  results provided by methods comparable to ours.}

@@

\begin{figure*}
\includegraphics[width=0.9\textwidth]{Fig0.pdf}
\caption{Fraction of halos in a mass bin that show a preferential
  alignment with respect to an eigenvector for the three properties
  studies in this paper: shape (major axis), angular momentum and
  peculiar velocity. Left column presents the results against the Tweb
  and the right the Vweb. Strong colors refer to $256^3$ grid
  resolutions and lighter colors to a $512^3$ grid.
\label{fig:preferential}}
\end{figure*}

Figure \ref{fig:preferential} presents all the results for the
preferential alignment (PA).

>>>>

\title[Cosmic web alignments with halos]{Cosmic web alignments with the shape, angular momentum and peculiar velocities of dark matter halos}  
\author[S. Contreras et al.]{
\parbox[t]{\textwidth}{\raggedright 
  Jaime E. Forero-Romero$^{1}$,
  Sergio Contreras$^{2}$,
  Nelson Padilla$^{2}$ 
}
\vspace*{6pt}\\
$^{1}$Uni A
$^{2}$Uni B
}
\maketitle

@@

{\bf Forero-Romero et al. (2014)} & T-Web & $0.5-1 \hMpc$ & 
filament &$++$ & $>10^{12}$\hMsun\\
&   & & 
filament & $+$ & $<10^{12}$\hMsun\\

&   & & 
wall & $++$ & $>10^{12}$\hMsun\\

&   & & 
wall & $+$ & $<10^{12}$\hMsun\\\hline

{\bf Forero-Romero et al. (2014)} & Vp-Web & $0.5-1 \hMpc$ & 
filament &$--$ & $>10^{12}$\hMsun\\
&   & & 
filament & none & $<10^{12}$\hMsun\\
&   & & 
wall & $--$ & $>10^{12}$\hMsun\\

&   & & 
wall & none & $<10^{12}$\hMsun\\\hline

@@

\end{tabular}\\
\caption{Shape alignment with the cosmic web. Summary of theoretical
  results provided by methods similar to ours.}
\end{table*}

@@

\cite{Codis2012} & Morse Theory \& T-Web & $1-5$ & 
filament & $--$ & $>10^{12.5}$\hMsun \\

&   & & 
filament & $++$ & $<10^{12.5}$\hMsun \\

@@

\end{tabular}
\caption{Spin alignment with the cosmic web. Summary of theoretical
  results provided by methods similar to ours.}

@@

\begin{figure*}
\includegraphics[width=0.9\textwidth]{Fig0.pdf}
\caption{Fraction of halos in a mass bin that show a preferential
  alignment with respect to an eigenvector for the three properties
  studies in this paper: shape (major axis), angular momentum and
  peculiar velocity. Left column presents the results against the Tweb
  and the right the Vweb. Strong colors refer to $256^3$ grid
  resolutions and lighter colors to a $512^3$ grid. The thick black
  horizontal line at $0.33$ corresponds to the expected fraction for a
  a random vector field.
\label{fig:preferential}}
\end{figure*}

Figure \ref{fig:preferential} presents all the results for the
preferential alignment (PA) summarizing to a good extent the main
results of this paper.

For shape alignment and the Tweb (upper row, right column) we find a strong
preferential alignment along the third eigenvector $\vec{e}_{3}$. This
signal incresases steadily with mass and is almost independent of the
grid resolution. At high masses between $70\%$ and $100\%$ of the
halos have their major axis aligned along $\vec{e}_{3}$ which means
that they mostly lie along filaments and sheets.

The shape alignment and the Vweb (upper row, left column) gives a
different perspective. Firstly, there seems to be little evidence
for an alignment for masses below $10^{11}-10^{12}$\hMsun, depending
on the grid resolution. Secondly, the alignment at higher masses goes
along the first eigenvector $\vec{e}_{1}$ meaning that they mostly lie
perpendicular to the filaments and sheets. In the discussion section
we clarify this result that at first might seem puzzling.

For fhe angular momentum alignment and the Tweb (middle row, right
column) we find that at low masses $<10^{12}$\hMsun no evidence for
any alignment. At higher masses $>10^{12}$\hMsun there is weak signal
of preferential alignment along the first and second eigenvectors,
between $35\%$ to $45\%$ of the halos are aligned with respect to
$\vec{e}_1$ and $\vec{e}_2$. Correspondingly, between $10\%$ to $20\%$
of the halos are aligned along respect to $\vec{e}_{3}$. This means
that most of the halos are perpendicular to the filaments and do not
have a clear alignment with respect to walls.

The angular momentum in the Vweb (middle row, left column) presents a
a signal of alignment along the second eigenvector $\hat{e}_{2}$,
between $45\%$ to $60\%$ of the halos are aligned along that
direction. While there is a minority of halos aligned with
$\vec{e}_{1}$.  There a clear change in trends around
$10^{11}$\hMsun-$10^{12}$\hMsun depending on the grid resolution;
below that mass range there is no evidence for alignment while at
higher masses appear all the trends we describe. This means that most
of the halos tend to lie along walls but do not have a clear alignment
with respect to filaments.
